Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel-overview.tex
ll

\section{$\tilde O(\sqrt{T})$ regret with $L$-level policy}
\label{sec:llevel}
In this section, we give an overview of how we extend our three-level
policy to an $L$-level policy for $L > 3$ in order to achieve a regret
rate of $O_K(\sqrt{T} \polylog(T))$. We provide two such policies. The
first policy achieves the root-$T$ regret rate with $O(\log \log T)$
levels.

% In Theorem \ref{thm:llevel-1}, we show our $L$-level policy. We can
% achieve nearly optimal regret $O_K(T^{1/2} \polylog(T))$ with
% $O(\log\log(T))$ levels.
\begin{theorem}
\label{thm:llevel-1}
For any $L > 3$, there exists an $L$-level disclosure policy with
regret $$O_K\left(T^{2^{L-1}/(2^L-1)} \polylog(T) \right).$$ In
particular, there exists a $O(\log\log(T))$-level recommendation
policy with regret $O_K(T^{1/2} \polylog(T))$.
\end{theorem}

% In Theorem \ref{thm:llevel-2}, we show a policy with
Our second policy achieves an instance-dependent regret
guarantee. This policy has the same info-graph structure as the first
one in Theorem \ref{thm:llevel-1}, but requires a higher number of
levels $L = O(\log(T/\log\log(T)))$ and larger group sizes. We will
bound its regret as a function of on the gap parameter $\Delta$ even
though the construction of the policy does not depend on $\Delta$. In
particular, this regret bound outperforms the one in Theorem
\ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$.  It
also has the desirable property that the policy does not conceal too
much information from agents---any agent $t$ observes a good fraction
of history in previous rounds.

\begin{theorem}
\label{thm:llevel-2}
There exists a $O(\log(T)/\log\log(T))$-level policy such that for
every multi-armed bandit instance with gap parameter $\Delta$, the
policy has regret $$O_K(\min(1/\Delta, T^{1/2})\polylog(T))$$
Moreover, under this policy, each agent $t$ observes a subhistory of
size at least $\Omega( t/\polylog(T))$.
\end{theorem}
\swcomment{think the theorem statement implies independence of
  $\Delta$}

Detailed proofs and discussions of Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2} can be found in Appendix \ref{sec:llevel-details}. Similarly as Section \ref{sec:3level}, we first prove them in the case of 2 arms (Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel}). We then extend them to the case of constant number of arms (Theorem \ref{thm:constarm}).

@@

\xhdr{Connecting structures between levels} In our 3-level
policy, the second level has $\NG = \Theta(\log(T))$ groups. We do so to
ensure that in the small gap case (Lemma \ref{3levelsmallcase}), with
high probability, both arms are pulled enough times in the second
level. The argument relies on the fact that agents in different
second-level groups observe disjoint histories of the first level and
the independent randomness in first level groups guarantees each arm
$a$ to have a ``lucky'' second-level group such that agents in that
group all pull arm $a$ with high probability.

>>>>

\section{$\tilde O(\sqrt{T})$ regret with $L$-level policy}
\label{sec:llevel}
In this section, we give an overview of how we extend our three-level
policy to a more adaptive $L$-level policy for $L > 3$ in order to
achieve a regret rate of $O_K(\sqrt{T} \polylog(T))$. We provide two
such policies. The first policy achieves the root-$T$ regret rate with
$O(\log \log T)$ levels.

% In Theorem \ref{thm:llevel-1}, we show our $L$-level policy. We can
% achieve nearly optimal regret $O_K(T^{1/2} \polylog(T))$ with
% $O(\log\log(T))$ levels.
\begin{theorem}
\label{thm:llevel-1}
For any $L > 3$, there exists an $L$-level disclosure policy with
regret $$O_K\left(T^{2^{L-1}/(2^L-1)} \cdot \polylog(T) \right).$$ In
particular, there exists a $O(\log\log(T))$-level recommendation
policy with regret $O_K(T^{1/2} \polylog(T))$.
\end{theorem}

% In Theorem \ref{thm:llevel-2}, we show a policy with
Our second policy achieves an instance-dependent regret
guarantee. This policy has the same info-graph structure as the first
one in Theorem \ref{thm:llevel-1}, but requires a higher number of
levels $L = O(\log(T/\log\log(T)))$ and larger group sizes. We will
bound its regret as a function of the gap parameter $\Delta$ even
though the construction of the policy does not depend on $\Delta$. In
particular, this regret bound outperforms the one in Theorem
\ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$.  It
also has the desirable property that the policy does not conceal too
much information from agents---any agent $t$ observes a good fraction
of history in previous rounds.

\begin{theorem}
\label{thm:llevel-2}
There exists a $O(\log(T)/\log\log(T))$-level policy such that for
every multi-armed bandit instance with gap parameter $\Delta$, the
policy has regret $$O_K(\min(1/\Delta, T^{1/2}) \cdot \polylog(T))$$
Moreover, under this policy, each agent $t$ observes a subhistory of
size at least $\Omega( t/\polylog(T))$.
\end{theorem}
\swcomment{think the theorem statement implies independence of
  $\Delta$}

In this section, we present the main techniques in our solution, and the 
full proofs of Theorem \ref{thm:llevel-1} and Theorem \ref{thm:llevel-2} will be deferred to Appendix \ref{sec:llevel-details}. Similarly as Section \ref{sec:3level}, we first prove them in the case of 2 arms (Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel}). We then extend them to the case of constant number of arms (Theorem \ref{thm:constarm}).

@@

\xhdr{Connecting structures between levels.} In our 3-level
policy, the second level has $\NG = \Theta(\log(T))$ groups. We do so to
ensure that in the small gap case (Lemma \ref{3levelsmallcase}), with
high probability, both arms are pulled enough times in the second
level. The argument relies on the fact that agents in different
second-level groups observe disjoint histories of the first level and
the independent randomness in first level groups guarantees each arm
$a$ to have a ``lucky'' second-level group such that agents in that
group all pull arm $a$ with high probability.
